```{r child = 'pre-chapter-script.Rmd'}
```

# Preface {-}

```{r child = 'README.md'}
```

-------

Because this book was built as a testbed\index{testbed} for "A Fresh Approach", it has a few things
purely intended to ensure proper operation of the technology.  Here
is one:

::: {.example #ex:prefaceex}
A numbered example in the preface that will be referenced later.
:::

## Preface page numbers

In published books, the preface should be part of the front matter, numbered with roman page numbers.
This book starts numbering the preface with Arabic.  It's quite easy to fix, just move the `\mainmatter`
command from the `index.Rmd` file to the start of the first content chapter.

The reason it's not just done already is that when you do a single-chapter build, it's nice to have arabic page numbers on your single chapter.
Keeping `\mainmatter` in the `index.Rmd` file accomplishes this.  I recommend developing the book with `\mainmatter` in the `index.Rmd` file, and
then near the time of publication move it to the start of chapter 1.

