# Basics {#basics}

## Labels and references
You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(literature). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(theorems).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

\index{iris}
```{r nice-tab}
knitr::kable(
  head(faithful, 5), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

## Fitting things on the page

### Side by side figures
You can put figures side by side using `out.width=c('50%','50%'), fig.show='hold'` options to r blocks.

```{r palettes, out.width=c('50%','50%'), fig.show='hold'}
library(RColorBrewer)
display.brewer.pal(n = 8, name = "Blues")
display.brewer.pal(n = 8, "Reds")
```

### Wide R output

What happens with R output and margins?

One long vector:
```{r wide}
discoveries
```

One wide matrix:
```{r wider}
matrix(runif(100), ncol = 20)
```

### Tidy source code
Here we deal with source code reformatting for prettier style.
This book has a global setting in `pre-chapter-script.R` that
runs all source code through the `styler` package.
Or you can do it on a chunk-by-chunk basis using the chunk options
`tidy='styler'` or `tidy=TRUE` to use `formatR`.

Enforcing line lengths needs to be done manually (for now, not supported by 
either `styler` or `formatR`)

```{r tossing}
X <- replicate(1000, { coin_toss <-sample(c("H","T"),3, replace= TRUE)
  sum(coin_toss == "H")})
mean(X >= 1)
```

## Footnotes and indexing

After spending all day getting henna designs drawn, she noticed she had a foot note.[^henna]

[^henna]: This joke (c) 2020 by Bryan Clair.

Index in LaTeX with `\index{Daft Punk}\index{music!Daft Punk}`:
This book features music by Daft Punk\index{Daft Punk}\index{music!Daft Punk} and poetry by Carl Sandburg\index{Sandburg, Carl}.
