# Final Words {#summary}

Please answer question @easy.  Question @easy should be and easy warmup for question @skills. Answer question @skills before trying question @hard.  Question @impossible doesn't actually exist.

::: example
This is an example.
:::

::: example
Another example.
:::

::: theorem
A theorem.
:::

::: definition
Let $A$ and $B$ be events in a sample space $S$. 

1. $A \cap B$ is the set of outcomes that are in  *both* $A$ and $B$.
2. $A \cup B$ is the set of outcomes that are in *either* $A$ or $B$ (or both).
3. $\overline{A}$ is the set of outcomes that are *not* in $A$ (but are in $S$). 
4. $A \setminus B$ is the set of outcomes that are in $A$ and not in $B$.
:::

::: example
Third example.
:::

::: definition
I like my TVs to have high definition.
:::

Now you're ready for questions @easy and @skills, but probably need to study more before working question @hard.

You might refer back to Theorem \@ref(thm:Lyapunov) if you want to learn.

## Exercises {-}

Question @easy is easy.

@easy. What is $S$?

Questions @hard and @impossible are harder.

@skills. Show $\overline{\overline{(A+B)}+C} = A \cap \overline{C} + B \cap \overline{C}$

@hard. Given a formula $F(A_1,\dotsc,A_n)$ made from $\cup$,$\cap$, and set complement, find events $A_1,\cdots,A_n$ so that the set $F(A_1,\dotsc,A_n)$ is nonempty.
```{r include=FALSE, cache=FALSE}
# This script is set to run automatically at the end of each chapter
# in the _bookdown.yml configuration file

#
# It automatically writes all packages to the end of the file "package-list.log"
# which was first created in the index.Rmd file
#
packs <- .packages()
if (!is.null(packs)) {
  packfile <- file("package-list.log","a")
  writeLines(packs,packfile)
  close(packfile)
}
```
```{r include=FALSE, cache=FALSE}
# This script is set to run automatically at the end of each chapter
# in the _bookdown.yml configuration file

#
# It automatically writes all packages to the end of the file "package-list.log"
# which was first created in the index.Rmd file
#
packs <- .packages()
if (!is.null(packs)) {
  packfile <- file("package-list.log","a")
  writeLines(packs,packfile)
  close(packfile)
}
```
